Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-01 paper/ms.tex
update ms

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust clumps in orbit at the
  Keplerian corotation radius.  Here, we report new CQVs discovered in
  TESS data collected between July~2018 and Sep~2022, and analyze
  their variability.  Our analysis of \nstarssearched\ K- and M-dwarfs
  with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.
  Most of these discoveries are new, and they include the brightest
  and closest examples of this class of object known ($T$$\approx$9.5;
  $d$$\approx$20\,pc), as well as the most massive
  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1000 cycles,
  but which in detail shows anywhere from four to eight local minima
  per cycle.  LP-502 at times demonstrated drastic shape changes over
  less than one cycle, and also displayed distinct superposed periods
  simultaneously.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating dust clumps are the most likely explanation.  In the
  future, we expect that our sample will facilitate modeling and
  observational efforts aimed at understanding these objects, and
  connecting them to the broader contexts of star, disk, and exoplanet
  evolution.  For instance, based on the rate of dip evolution, we
  estimate that the incident dust flux corresponds to of order an
  asteroid belt's worth of mass accreting onto these stars over $10^8$
  years.
\end{abstract}

@@

% NOTE: could write this more from a stellar evolution angle.
% M-dwarfs contract.  They spin up.  Some reach rapid rotation rates,
% and exhibit strong magnetic fields.

@@

In our view, the arguments seem best established for the dust clump
hypothesis \citep{2023MNRAS.518.4734S}.  This is primarily because the
prominence scenario lacks a mechanism for generating broadband
opacity, and the screen scenario is inconsistent with the degree of
observed periodicity, the lack of infrared excess, and the observed
lifetime of the effect, which is an order of magnitude longer than the
$\approx$$10^7$ years timescale typically quoted for the primordial
disk to disperse (CITE).  However, unambiguous evidence, for instance
a spectroscopic detection of silicates during a ``dip'', has yet to be
acquired.

@@

A point on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses whose optical variability is linked
to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
introducing yet another standard, we prefer a nomenclature that
reflects how, when observed over timescales of more than tens of
cycles, CQVs are never exactly periodic.  Their shapes evolve, usually
with some coherence timescale, similar to variability induced by
surface inhomogeneities such as starspots.  While the three-type
classification scheme proposed by \citet{2017AJ....153..152S} may
indeed provide some helpful visual distinctions amongst CQV
sub-classes, it seems likely that they are all explained by a single
underlying phenomenon, and so we opt to refer to them by a single
empirically descriptive name.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
		the stability of the dips, the lack of observed infrared
		excesses, and the challenge of producing broadband opacity variations
		with only ionized hydrogen in the prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  Specifically, we adopted the ``BT-Settl''
stellar atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.
The broadband magnitudes we considered included $GG_{\rm BP}G_{\rm
RP}$ from Gaia DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$
from Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We
specifically omitted UV flux measurements to avoid biasing our fit
with any possible chromospheric UV excess.
\texttt{astroARIADNE} compares the measured broadband flux measurements
against pre-computed model grids, and by default fits for six
parameters:
$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
The distance  prior is drawn from \citet{2021AJ....161..147B}.
The surface gravity and metallicity are generally unconstrained.
And finally, given our particular use-case, 
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.
Using \texttt{Dynesty} \citep{2020MNRAS.493.3132S},
we statically sampled the posterior probability assuming the default
Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
\mathcal{Z} < 0.01$, where $\mathcal{Z}$ denotes the evidence.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.
      Gray are raw 2-minute data;
			black bins to 300 points per cycle.  Each panel is labelled by
      the TIC identifier, the TESS sector number, and the period in hours.
      Objects are ordered such that sources with the most TESS data available are
       on top (see Section~\ref{sec:catalog}).
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
search, along important physical and observational properties.
\ngoods\ objects demonstrate what we view as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector, and
we refer to these as the ``gold sample''.  The remaining \nmaybes\ CQV
candidates were ambiguous (in our view), and their variability might
be caused by say, multiple starspot groups.  Additional data from TESS
or other instruments can help resolve their classification; in
Section~\ref{subsec:irexcess} below for instance we discuss a few
cases in this ambiguous sample that after additional analysis were
clarified as dippers.  We also emphasize that our initial
classifications were based on whether {\it any} TESS sectors showed
evidence for the CQV phenomenon.

The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
for the \ngoods\ bonafide CQVs.  The objects are sorted first in order
of the number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The objects at the top therefore have the most 120-second
cadence data.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, while the slowest five span
27\,hr$<$$P$$<$38\,hr.

In terms of the light curve shapes, Figure~\ref{fig:singlemosaic}
shows a broad range of variability, with anywhere from two to eight
local minima per cycle.  Some stars show relatively ordinary
modulation during one continuous portion of the phased light curve,
and highly structured modulation in the remainder of the cycle (e.g.
TIC~206544316, TIC~224283342, TIC~402980664).  Others show structured
modulation over the entire span of a cycle (e.g. TIC~2234692,
TIC~401789285, TIC~425933644, TIC~142173958).  Others still show some
mix between these two modes.

A small number of objects at first glance seem reminiscent of
eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In the
few such cases, we believe that that are unlikely to be eclipsing
binaries due to additional coherent variations in the light curves
that are distinct from any binary phenomenology of which we are aware.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were confidently associated with a nearby moving group or open cluster
using BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
in Sco-Cen (LCC / UCL / USco) is not surprising, since Sco-Cen
contains the majority of pre-main-sequence stars in the solar
neighborhood.  The absence of CQVs in IC\,2602 and IC\,2391 can be
understand by those clusters being beyond 100\,pc, where the
completeness of the TESS 120-second cadence data is below 10\%; based
on the abundance of CQVs in the 40\,Myr Tuc-Hor and Columba, the
similarly-aged IC\,2602 and IC\,2391 clusters should show a large
number of CQVs in the TESS full frame image data.

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2022arXiv221109822B}).  For the other two
(TIC~58084670 and TIC~141146667), we are convinced of both their CQV
status and their youth, but we were not able to confidently associate
either star with any young groups.  Both objects were noted as being in the
``diffuse'' Class~III YSO population near the Sun by \citet{2021ApJ...917...23K}.
That diffuse population may contain kinematic structures that have yet
to be unravelled.  However, the absence of obvious young, co-moving
stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$ of
our two CQVs suggest that they may have ``run away'' from their birth
locations.

The CQV phenomenon persists at least up to 150\,Myr.  Our catalog
includes three $\approx$150\,Myr old AB Dor members (TIC~288344202,
TIC~332517282, and TIC~368129164), a $\approx$112\,Myr old Pleiades
member (TIC~440725886; \citealt{CantatGaudin_2020}), and a
similarly-aged Psc-Eri member (TIC~38539720;
\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
was the previous record-holder for oldest-known CQV
\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
unambiguous case (EPIC~211070495) and a few other candidates were also
previously known in the Pleiades \citep{2016AJ....152..114R}.  While
we expect to have been sensitive to CQVs in the nearby Hyades
($\approx$700\,Myr), again due to the specifics of the TESS 120-second
selection function, we do not know at this time whether we would have
been sensitive to such stars.

@@

As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
catalog did not show infrared excesseses in the WISE1-4 bands.
Visually inspecting the SEDs, we labelled two objects as having
``good'' infrared excesses (both W3 and W4), and three as ``possible''
infrared excess.

The two ``good'' IR excesses were TIC~193136669 (TWA~34) and
TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
($\approx$10\,Myr), and have ``long'' periods of 38\,hr and 44\,hr
respectively.  In our initial labelling, we labelled both as ``maybe''
CQVs because the dips in their light curves did not show the rigid
periodicity typical of CQVs;  their periods were also relatively
long.  After labelling them, we learned that TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It has also been labelled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, but
nonetheless leave it in our catalog as an indication of possible
ambiguities in our search process.  TIC 57830249 (TWA~33) also has
previously detected 1.3\,mm continuum emission
\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
present.  It therefore probably also a dipper that snuck its way into
our ``maybe'' pile.

Our three ``possible'' infrared excesses were TIC~405910546,
289840926, and 244161191.  After a literature search, we concluded
that none have clear evidence for the presence of a disk.
TIC~405910546, in LCC, shows a unique TESS light curve, reminescent of
a $P$=38\,hr singly-eclipsing binary, except with additional
substructure during each eclipse that resembles the CQV phenomenon
more than any other variability of which we are aware.  TIC~289840926
($\beta$~Pic moving group, $P$=4.8\,hr), show what we believe is a
clear CQV signals, but has no definitive evidence for a large, dusty
disk.  TIC~244161191 (hilariously, TOI-278), in Columba, also has no
definitive evidence for a large disk.  It is however
``multi-periodic''---in addition to the 7.17\,hr CPV signal, there is
a superposed 8.39\,hr sinusoidal signal, probably from an unresolved
binary neighbor.

Comparing these results against the backdrop of our increasing
understanding of dippers
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
it is clear that the loss of an infrared excess is associated with
strong changes in a star's optical variability.  It is not
unreasonable to imagine connections between CQVs and dippers: both
classes of object can show transient flux dips that are relatively
narrow in duration.  Such dips are probably caused by clumps of dust.
However the CQV dips are typically {\it i}) more periodic and {\it
ii}) less deep than those of dippers, and {\it iii}) they display far
less transience over timescales of a few to tens of cycles.  At a
population level, the CQV stars are also older.  A shared mystery
between the CQVs and dippers, in our own estimation however, is the
exact mechanism that produces the {\it narrowness} of the dust clumps
in certain cases.  It is not unreasonable to imagine a similar
mechanism operating for both types of object, tied perhaps to a shared
magnetic topology, or perhaps to a preference for dust to inspiral to
the star in clumps from tidally disrupted infalling bodies.

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.
Such a baseline was available for 32 of the \ngoods\ CQVs in our
catalog; for plotted purposes we show the brightest 27.
Of these 27 CQVs,
a few show clear signs of the phenomenon in one sector,
and marginal or non-existence signs in the other.
While there is some subjectivity in this assessment, to our eye
cases for which at least one sector would be flagged as ``ambiguous'' include
TIC~368129164 (S23 might be labelled an EB),
TIC~193831684 (which has been erroneously labelled an EB CITE Albrecht paper),
TIC~177309964 (S38 would be simply a rotating star),
TIC~404144841 (S38 looks like a rotating star),
TIC~201898222 (S3 looks like a rotating star),
TIC~144486786 (S32 might be flagged as a possible RS CVn),
TIC~38820496 (S28 might be a possible RS CVn).
One could easily also imagine in cases like TIC~206544316 that if
observed at lower signal to noise, the drastic shape evolution would
not be appreciated.
We emphasize that the periods themselves were all stable to $<$0.1\%.
Broadly speaking, this shape evolution
suggests that CQVs have a duty cycle of $\approx$75\%.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f3.pdf}
		\vspace{-0.6cm}
		\caption{
		{\bf CQVs keep their periods but change their shapes.}
      32 of our \ngoods\ CQVs from Figure~\ref{fig:singlemosaic} 
      had 120-second cadence TESS data available for
      a baseline of at least two years; the 27 brightest are shown here.
      Each panel shows one sector of TESS data, and is phased to its deepest minimum in flux.
      Each panel's title shows the TIC identifier and approximate period in hours.
      Text insets show the TESS sector numbers, which generally span two years, or at least
      1{,}000 cycles.
      The vertical scale is fixed across sectors to clarify shape changes.
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

\paragraph{Extremes}
The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), which is a likely member of AB Dor.  To our knowledge,
this manuscript is the first time that it has been noted as a CQV.

@@

The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~50745567.
There are a number of other similar very low mass stars, which
suggests the phenomenon may extend into the brown dwarf regime.

The three brightest CQVs in Table are DG~CVn ($T$=9.3), TIC~405754448
($T$=9.6), and TIC~167664935 ($T$=10.3).

>>>>

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at the
  Keplerian corotation radius.  Here, we report new CQVs discovered in
  TESS data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs
  with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.
  Most of these discoveries are new, and they include the brightest
  and closest examples of this class of object known ($T$$\approx$9.5;
  $d$$\approx$20\,pc), as well as the most massive
  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000 cycles,
  but which in detail shows anywhere from four to eight local minima
  per cycle.  LP-502 at times demonstrated drastic shape changes over
  less than one cycle, and also displayed distinct superposed periods
  simultaneously.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most likely explanation.  In the
  future, we expect that our sample will facilitate modeling and
  observational efforts aimed at understanding these objects, and
  connecting them to the broader contexts of star, disk, and exoplanet
  evolution.
%  For instance, based on the rate of dip evolution, we
%  estimate that the incident dust flux corresponds to of order an
%  asteroid belt's worth of mass accreting onto these stars over $10^8$
%  years.
\end{abstract}

@@

@@

In our view, the arguments seem best established for the dust clump
hypothesis \citep{2023MNRAS.518.4734S}.  This is primarily because the
prominence scenario lacks a mechanism for generating broadband
opacity, and the screen scenario is inconsistent with the degree of
observed periodicity, the lack of infrared excess, and the observed
lifetime of the effect, which is an order of magnitude longer than the
$\approx$$10^7$ year timescale typically quoted for the primordial
disk to disperse.  However, unambiguous evidence, for instance a
spectroscopic detection of silicates during a ``dip'', has yet to be
acquired.

@@

A word on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses whose optical variability is linked
to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
introducing yet another standard, we prefer a nomenclature that
reflects how, when observed over timescales of more than tens of
cycles, CQVs are almost, but not exactly periodic.  Their shape
evolution implies that they are irregularly periodic, or for short,
quasiperiodic.  While the three-type classification scheme proposed by
\citet{2017AJ....153..152S} may indeed provide some helpful visual
distinctions amongst CQV sub-classes, it seems likely that they are
all explained by a single underlying phenomenon, and so we opt to
refer to them by a single empirically descriptive name.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
    the stability of the dips, their chromaticity, the lack of
    observed infrared excesses, and the challenge of producing
    broadband opacity variations with only ionized hydrogen in the
    prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the ``BT-Settl'' stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We specifically omitted UV flux measurements to
avoid biasing our fit with any possible chromospheric UV excess.
\texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters:
$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
The distance  prior is drawn from \citet{2021AJ....161..147B}.  The
surface gravity and metallicity are generally unconstrained.  And
finally, given our particular use-case, we assumed the following
priors for the temperature, stellar size, and extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  Using \texttt{Dynesty}
\citep{2020MNRAS.493.3132S}, we statically sampled the posterior
probability assuming the default Gaussian likelihood, and set a
stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$, where
$\mathcal{Z}$ denotes the evidence.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.  Gray are raw 2-minute data; black bins to 300 points per
      cycle.  Each panel is labelled by the TIC identifier, the TESS
      sector number, and the period in hours.  Objects are ordered
      such that sources with the most TESS data available are on top
      (see Section~\ref{sec:catalog}).
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
search, along important physical and observational properties.
\ngoods\ objects demonstrated what we viewed as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector;
we refer to these as the ``gold sample''.  We found the remaining \nmaybes\ CQV
candidates to be ambiguous; their variability might
be caused by say, multiple starspot groups.  Additional data from TESS
or other instruments could help resolve their classification.  In the
following discussion, we will primarily restrict our discussion to the 
gold sample.

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves
for the \ngoods\ bonafide CQVs.  The objects are sorted first in order
of the number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The objects at the top generally have the most 120-second
cadence data.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, while the slowest five span
27\,hr$<$$P$$<$38\,hr.

In terms of the light curve shapes, Figure~\ref{fig:cqvs}
shows a broad range of variability, with anywhere from two to eight
local minima per cycle.  Some stars show relatively ordinary
modulation during one continuous portion of the phased light curve,
and highly structured modulation in the remainder of the cycle (e.g.
TIC~206544316, TIC~224283342, TIC~402980664).  Others show structured
modulation over the entire span of a cycle (e.g. TIC~2234692,
TIC~401789285, TIC~425933644, TIC~142173958).  Others still show some
mix between these two modes.

A small number of objects at first glance seem reminiscent of
eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In these
few cases, we believe that that are unlikely to be eclipsing binaries
due to additional coherent variations in the light curves that are
distinct from any binary phenomenology of which we are aware.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
in Sco-Cen is not particularly surprising, since Sco-Cen contains the
majority of pre-main-sequence stars in the solar neighborhood.
However it is certainly likely given the $\lesssim$$10\%$ completeness
of TESS beyond 100\,pc that far more CQVs remains to be discovered in
Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
100\,pc, are an example of this completeness effect: no CQVs appear in
those clusters from our search.

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  However both do seem to
clearly show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  For instance,
both were noted as being in the ``diffuse'' Class~III YSO population
near the Sun by \citet{2021ApJ...917...23K}.

Our catalog confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Our catalog includes three $\approx$150\,Myr CQVs
in AB~Dor \citep{2015MNRAS.454..593B}: TIC~288344202, TIC~332517282,
and TIC~368129164.  There is also a $\approx$112\,Myr old Pleiades CQV
(TIC~440725886; \citealt{2015ApJ...813..108D,CantatGaudin_2020}), and
a similarly-aged Psc-Eri member (TIC~38539720;
\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
was the previous record-holder for oldest-known CQV
\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
unambiguous case (EPIC~211070495) and a few other candidates were also
previously known in the Pleiades \citep{2016AJ....152..114R}.  While
we expect to have been sensitive to CQVs in the nearby Hyades
($\approx$700\,Myr), again due to the specifics of the TESS 120-second
selection function, we do not know at this time whether we would have
been sensitive to such stars.

@@

As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
catalog did not show infrared excesseses in the WISE1-4 bands.
Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
we labelled two objects as having ``good'' infrared excesses (both W3
and W4), and three as ``possible'' infrared excess.

The two ``good'' IR excesses belonged to ``candidate'' CQVs
TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
Hydrae association ($\approx$10\,Myr), and have relatively long
periods of 38\,hr and 44\,hr respectively.  In our initial labelling,
we labelled both as ``maybe'' CQVs because the dips in their light
curves did not show the rigid periodicity typical of CQVs;  their
periods were also relatively long.  After labelling them, inspection
of further sectors clarified that both sources are dippers (see plots
in Appendix~\ref{app:vetting}).  In addition, TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labelled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, but
nonetheless leave it in our catalog as an indication of possible
ambiguities in our search process.  TIC 57830249 (TWA~33) also has
previously detected 1.3\,mm continuum emission
\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
present.  It therefore also a dipper that snuck its way into our
``maybe'' pile.

Our three ``possible'' infrared excesses were TIC~405910546,
289840926, and 244161191.  After a literature search, we concluded
that none have clear evidence for the presence of a disk.
TIC~405910546, in LCC, shows a unique TESS light curve, reminescent of
a $P$=38\,hr singly-eclipsing binary, except with additional
substructure during each eclipse that resembles the CQV phenomenon
more than any other variability of which we are aware.  TIC~289840926
($\beta$~Pic moving group, $P$=4.8\,hr), show what we believe is a
clear CQV signals, but has no definitive evidence for a large, dusty
disk.  TIC~244161191 (hilariously, TOI-278), in Columba, also has no
definitive evidence for a large disk.  It is however
``multi-periodic''---in addition to the 7.17\,hr CPV signal, this
source shows a superposed 8.39\,hr sinusoidal signal, probably from an
unresolved neighboring star.

Comparing these results against the backdrop of our increasing
understanding of dippers
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
it is clear that the loss of an infrared excess is associated with
strong changes in a star's optical variability.  It is reasonable to
imagine connections between CQVs and dippers: both classes of object
can show transient flux dips that are relatively narrow in duration.
Such dips are probably caused by clumps of dust.  However the CQV dips
are typically {\it i)} more periodic and {\it ii)} less deep than
those of dippers, and {\it iii}) they display far less transience over
timescales of a few to tens of cycles.  This is probably because CQV
stars have demonstrably less dust than dipper stars.  At a population
level, the CQV stars are also older.  A common mystery between the
CQVs and dippers, in our own estimation, is how exactly the {\it
narrowness} of the dust clumps is produced.  It is not unreasonable to
imagine a similar mechanism operating for both types of object, tied
perhaps to a shared magnetic topology, or perhaps to a preference for
dust to inspiral to the star in clumped structures.

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
the brightest 27.
Of these 27 CQVs, a few show clear signs of the phenomenon in one
sector, and marginal or non-existence signs in the other.
While there is some subjectivity in this assessment, to our eyes cases
for which at least one sector would be flagged as ``ambiguous''
include
TIC~368129164 (Sector 23 might be labelled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labelled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label!  Based on the
the shape evolution between Sectors 13 and 39 however, it is a CQV.
One could easily also imagine in cases like TIC~206544316 that if
observed at lower signal to noise, the drastic shape evolution would
not be appreciated.  We emphasize that the periods themselves were all
stable to $<$0.1\%.  Broadly speaking, this shape evolution suggests
that CQVs have an ``on/off'' duty cycle of $\approx$75\%.  This type
of correction is likely worth including in population-level estimates
of how intrinsically common CQVs are in the low-mass stellar
population \citep[e.g.][]{2022AJ....163..144G}.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f3.pdf}
		\vspace{-0.6cm}
		\caption{
		{\bf CQVs keep their periods but change their shapes.}
      32 of our \ngoods\ CQVs from Figure~\ref{fig:cqvs} had
      120-second cadence TESS data available for a baseline of at
      least two years; the 27 brightest are shown here.  Each panel
      shows one sector of TESS data, and is phased to its deepest
      minimum in flux.  Each panel's title shows the TIC identifier
      and approximate period in hours.  Text insets show the TESS
      sector numbers, which generally span two years, or at least
      1{,}000 cycles.  The vertical scale is fixed across sectors to
      clarify shape changes.
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

\subsection{Extremes}
The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), which is a likely member of AB Dor.  To our knowledge,
this manuscript is the first time that it has been noted as a CQV.
The three brightest CQVs we have found are DG~CVn ($T$=9.3),
TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).

@@

The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~267953787.
The catalog contains a few other stars with similar mass, which
suggests the phenomenon may extend into the brown dwarf regime.
